CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

Since we are generating networks across cohorts and sexes, identifiying conserved clusters using standard methods becomes non-trivial.  Instead of defining clusters for each subset and evaluating the difference, we first compute the differences in the correlation networks, then identify a single set a clusters based on this meta-network.  Then use sLED test on difference network, or use boxM_permute on original residuals, but with consensus clusters.

@@

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

df_genes = data.frame(ENSEMBL = geneEnsID, stringsAsFactors=FALSE) %>% getGeneSymbol('ENSEMBL')
table(df_genes$Chrom)

@@

```{r sex.confounding}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

@@

@@

@@

```{r testing.Dx_Sex}
# Hypothesis testing     
df_test.Dx_Sex = test_differential_correlation_interaction(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx_Sex, METADATA, nperm=100)  
```

## Discovery cohort
```{r plot.discovery.Dx_Sex}
# plot discovery and testing.  
ggplot(df_test.Dx_Sex, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

@@

```{r modules.in.second.cohort.Dx_Sex, fig.width=8, fig.height=100}

@@

	plot_grid(fig1, fig2, fig2, ncol=1)
	})

>>>>

Since we are generating networks across cohorts and sexes, identifiying conserved clusters using standard methods becomes non-trivial.  Instead of defining clusters for each subset and evaluating the difference, we first compute the differences in the correlation networks, then identify a single set of clusters based on this difference-network.  Then use hypothesis test of differential correlation in the second cohort to get p-value.

@@

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(zenith) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

df_genes = data.frame(ENSEMBL = geneEnsID, stringsAsFactors=FALSE) %>% getGeneSymbol('ENSEMBL')
# table(df_genes$Chrom)

@@

```{r load.go}
# Load Gene Ontology database 
go.gs = get_GeneOntology()
```

```{r sex.confounding, fig.width=5, fig.height=20}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
res = lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

@@

## Module enrichment
```{r top.enrich.Dx}

enrich.test = function(df_module, gs){

	res = lapply( unique(df_module$Module), function(mod){

			genes = df_module[df$]

		})

}

```

@@

rm(net.Dx_Sex) # saving this to disk is slow, so just delete it

@@

```{r testing.Dx_Sex}
# Hypothesis testing     
df_test.Dx_Sex = test_differential_correlation_interaction(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx_Sex, METADATA, nperm=1000)    
```

## Discovery cohort
```{r plot.discovery.Dx_Sex}
# plot discovery and testing.  
ggplot(df_test.Dx_Sex, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed"). 
```

@@

figList = lapply(df_test$Module[1:5], function(mod){.

@@

```{r modules.in.second.cohort.Dx_Sex, fig.width=8, fig.height=80}

@@

	plot_grid(fig1, fig2, fig3, ncol=1)
	})
